% Then you can run:  pdfcsplain your-file

\input ctustyle   % The template is included here.
\input pdfuni    % Uncomment this if you need accented PDFoutlines
\input opmac-bib % Uncomment this for direct reading of .bib database files 

\worktype [M/EN]

\faculty    {F3} 
\department {Department of Computer Science}
\title      {Learning to play real-time strategy games from demonstration using decentralized MAS}
\author     {Jan Malý}
\date       {May 2017}
\supervisor {RNDr. Michal Čertický, Ph.D.}  % One or more supervisors
\studyinfo  {Study Programme: Open informatics}  % Study programme etc.
\studyinfoadd  {Field of Study: Artificial Intelligence}  % Study programme etc.
\titleCZ    {Učení se hraní strategických her reálného času z demonstrací s využitím decentralizovaného MAS}
\pagetwo    {}  % The text printed on the page 2 at the bottom.
\specification {\picw=\hsize \cinspic agreement.jpg }

\abstractEN {
Despite the amount of effort put in Artificial Intelligence research, bots for real-time strategy games present no threat for professional human players. There are still many challenges to overcome by researchers to develop AI able to beat experts. In this work, we deal with three challenges: adaptive planning, domain knowledge integration and integration of AI techniques to unified architecture. We introduce the usage of Inverse Reinforcement Learning as a new approach for decision-making based on the observation human gameplay. To be able to integrate Inverse Reinforcement Learning with other techniques needed for the complete bot, we build our AI on new unified architecture in the form of a highly decentralized Multi-agent system. After using a small set of replays, our bot was able to learn strategy which beats built-in AI in some scenarios. The bot also shows the ability to adapt its behavior to the situation. The approach presents a novel way of developing challenging bots with little to none domain expert knowledge.
}
\abstractCZ {
Přes úsilí vynaložené na výzkum Umělé Inteligence, boti do strategických her reálného času nedokáží ohrozit profesionální lidské hráče. Stále je tu spousta výzev, které výzkumníci musí překonat, aby AI mohla prazit experty. V této práci se zabíváme třemi výzvami: adaptivním plánováním, integrací doménové znalosti a integrací AI technik do jednotné architektury. Představujeme použití techniky Inverse Reinforcement Learning jako způsobu, jak se naučit dělat rozhodnutí na základě pozorování her hraných hráči. Abychom mohli integrovat Inverse Reinforcement Learning společně s dalšími technikami vyžadovanými pro realizaci kompletního bota, postavili jsme naší AI na nové jednotné architektůře v podobě vysoce decentralizovaného Multi-agentního systému. Potom, co jsme použili malou množinu ukázek her, náš bot se by shopný naučit strategii, která dokáže v některých scénářích porazit zabudovanou AI. Bot také vykazuje schopnost uzpůsobit své chování situaci. Náš přístup demonstruje nový způsob jak s minimem doménových znalostí vyvíjet bota, který bude výzvou pro lidské hráče.
}           % If your language is Slovak use \abstractSK instead \abstractCZ

\keywordsEN {%
Inverse Reinforcement Learning; Multi-agent system; real-time strategy game; bot
}
\keywordsCZ {%
Inverse Reinforcement Learning; Multiagentní system; strategie reálného času; bot
}
\thanks {           % Use main language here
I would like to thank my supervisor Michal Čertický for the valuable comments
and remarks he has given me during the
creation of this work.
}
\declaration {      % Use main language here
   Prohlašuji, že jsem předloženou práci vypracoval
   samostatně a že jsem uvedl veškeré použité informační zdroje v~souladu
   s~Metodickým pokynem o~dodržování etických principů při přípravě
   vysokoškolských závěrečných prací.

   V Praze dne 26. 5. 2017 % !!! Attention, you have to change this item.
   \signature % makes dots
}

%%%%% <--   % The place for your own macros is here.

%\draft     % Uncomment this if the version of your document is working only.
%\linespacing=1.7  % uncomment this if you need more spaces between lines
                   % Warning: this works only when \draft is activated!
%\savetoner        % Turns off the lightBlue backround of tables and
                   % verbatims, only for \draft version.
%\blackwhite       % Use this if you need really Black+White thesis.
%\onesideprinting  % Use this if you really don't use duplex printing. 


\makefront  % Mandatory command. Makes title page, acknowledgment, contents etc.

\input intro
\input rts_subproblems_and_starcraft_specifics
\input related_work_challenges
\input IRL
\input multiagent_systems
\input designing_multi_agent_system_and_integrating_learning_to_it
\input empirical_evaluation
\input conclusion

\input prilohy % bibliography

\bye
